Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2019-07-28 ms/manuscript.Rmd
Add check of model residuals with Moran's I

We calculated daily maximum, mean, minimum, and standard variation of temperature, RH, and VPD for each site from the raw climate data, then overall means from the daily values. We analyzed correlation between the mean values with Pearson's correlation coefficient, and retained a set with correlation coefficients less than 0.9 (hereafter, "climatic variables"). Variables relating to VPD, which have no meaning if less than zero, and some other variables that had skewed distributions, were square-root transformed prior to fitting models. We tested for differences between epiphytic and terrestrial dataloggers while accounting for elevation with ANCOVA, using growth habit as the categorical variable and elevation as the covariate. We identified the best-fitting linear model for each climatic variable in response to growth habit and elevation by constructing a set of models including the effect of each independent variable alone and their interactions, then selecting the one with the lowest Akaike Information Criterion (AIC). A single outlier site with unusually high temperature and low humidity (Mt. Rotui, 830 m) site was excluded from ANCOVA and linear models. Mt. Rotui is an isolated peak with greater exposure than the other two mountains where the rest of the plots were established, which are part of a mountain complex on the interior of the island.

@@

Prior to testing for differences in diversity metrics, we first checked for correlation between metrics with Pearson's correlation coefficient, and retained a set of metrics with absolute correlation coefficients < 0.9. We tested for differences between epiphytic and terrestrial communities with a paired \tval-test. We simultaneously tested the effects of environment and growth habit on diversity metrics using a full-subsets multiple regression approach with general additive models (GAMs) as implemented in the \package{FSSgamm} R package [@Fisher2018]. For each diversity metric, we built a set of models (Gaussian family, with site as a random effect) taking into account all combinations of explanatory variables and their pairwise interactions, and ranked these by corrected AIC (AICc) to find the models that best explain the data. Our dataset included `r nrow(div_metrics_select) - nrow(climate_select)` communities that lacked climate data and could not be included in full-subsets multiple regression analysis. Since we found that all climatic variables are related to elevation (see Results), we also constructed linear models for each diversity metric using same model selection procedure as in the climate analysis.

>>>>

We calculated daily maximum, mean, minimum, and standard variation of temperature, RH, and VPD for each site from the raw climate data, then overall means from the daily values. We analyzed correlation between the mean values with Pearson's correlation coefficient, and retained a set with correlation coefficients less than 0.9 (hereafter, "climatic variables"). Variables relating to VPD, which have no meaning if less than zero, and some other variables that had skewed distributions, were square-root transformed prior to fitting models. We tested for differences between epiphytic and terrestrial dataloggers while accounting for elevation with ANCOVA, using growth habit as the categorical variable and elevation as the covariate. We identified the best-fitting linear model for each climatic variable in response to growth habit and elevation by constructing a set of models including the effect of each independent variable alone and their interactions, then selecting the one with the lowest corrected Akaike Information Criterion (AIC~c~) [@Akaike1973]. A single outlier site with unusually high temperature and low humidity (Mt. Rotui, 830 m) site was excluded from ANCOVA and linear models. Mt. Rotui is an isolated peak with greater exposure than the other two mountains where the rest of the plots were established, which are part of a mountain complex on the interior of the island (J. Nitta, pers. obs.).

@@

We checked for correlation between diveristy metrics with Pearson's correlation coefficient, and retained a set of metrics with absolute correlation coefficients < 0.9. We tested for differences in diversity metrics between epiphytic and terrestrial communities with a paired \tval-test. We simultaneously tested the effects of climate and growth habit on diversity metrics using a full-subsets multiple regression approach with general additive models (GAMs) as implemented in the \package{FSSgamm} R package [@Fisher2018]. For each diversity metric, we built a set of models (Gaussian family, with site as a random effect) taking into account all combinations of explanatory variables and their pairwise interactions, and ranked these by AIC~c~ to find the models that best explain the data. Our dataset included `r nrow(div_metrics_select) - nrow(climate_select)` communities that lacked climate data and could not be included in full-subsets multiple regression analysis. Since we found that all climatic variables are related to elevation (see Results), we also constructed linear models for each diversity metric using the same model selection procedure as in the climate analysis. We checked for spatial autocorrelation in the model residuals with Moran's *I* [@Moran1950] as implemented in the \package{spdep} R package [@Bivand2013].
